---
title: "HW1"
author: "GuillermoSchneider"
date: "2024-02-02"
output: html_document
---


# Introduction
 
## https://fivethirtyeight.com/features/what-makes-our-new-2020-democratic-primary-polling-averages-different/

 The article covers FiveThirtyEight’s democratic primary polling averages method in the 2020 election, and why they think they've created a better method. They adjust state polls based on trends in national polls, pollster bias and included pollster ratings weights, and finally putting more weight on polling changes after a major news event. 

**Loaded the csv from github raw into data frame in r:**
```{r}
polling<-read.csv("https://raw.githubusercontent.com/GuillermoCharlesSchneider/HW1/main/pres_primary_avgs_1980-2016.csv", header= TRUE, sep=",")
```

**renamed columns:**
```{r}
colnames(polling) <- c("RaceYearAndParty", "State", "ModelDate","CandidateName","Candidate_ID","Estimate","Trend_Adjusted", "Timestamp", "OneDayTest", "Contest_Date")
```

**subset of just iowa polling:**
```{r}
IowaPolling <- subset(polling, State == "Iowa")
```


### Conclusion
I successfully pulled in the data
