---
title: "sentiment_analysis"
author: "GuillermoSchneider"
date: "2024-03-08"
output: html_document
---

```{r}
#install.packages("tidytext")
#install.packages("textdata")
#install.packages("tidyverse")
#install.packages("wordcloud")
library(tidytext)
library(textdata)
library(tidyverse)
library(wordcloud)

```

##https://www.tidytextmining.com/sentiment


**AFINN from Finn Årup Nielsen**
```{r}
get_sentiments("afinn")
```

**bing from Bing Liu and collaborators**
```{r}
get_sentiments("bing")
```

**nrc from Saif Mohammad and Peter Turney**
```{r}
get_sentiments("nrc")
```


**sample of 8000 posts from lucas**
```{r}
test_scrape <- read.csv("https://raw.githubusercontent.com/GuillermoCharlesSchneider/DATA-607/main/Project-3/test_scrape.csv")
```



```{r}
Skills <- read.csv("https://raw.githubusercontent.com/GuillermoCharlesSchneider/DATA-607/main/Project-3/skills.csv")

```




```{r}

clean_scrape <- test_scrape[] 
tidy_scrape <- test_scrape %>%
  unnest_tokens(word, comment)
```



```{r}
nrc_joy <- get_sentiments("nrc") %>% 
  filter(sentiment == "joy")
```


```{r}
tidy_scrape %>%
  inner_join(nrc_joy) %>%
  count(word, sort = TRUE)
```

```{r}
Skills$word <- tolower(Skills$Skills)

tidy_scrape %>%
  inner_join(Skills) %>%
  count(word, sort = TRUE)
```


```{r}
t <- tidy_scrape %>%
  count(word, sort = TRUE)
```


search through reddit comments, group the skills thatre are 2 words

skills one word
Search for comments that include those words
see what positive or negative words are around in those comments
score?
see which topics have more negative postive score?
weight it by the relevancy?



nrc from Saif Mohammad and Peter Turney -> word cloud


sentiment analysis over time, we have the reddit dates, positive minus negative

list the courses that we scraped

?????
```{r}
library(wordcloud)
w <- sort(rowSums(t), decreasing = TRUE)
set.seed(222)
wordcloud(word = word(w),
          freq = w,
          max.words = 150,
          random.order = F,
          min.freq = 5,
          colors = brewer.pal(8, 'Dark2'),
          scale = c(5, 0.3),
          rot.per = 0.7)
```

