---
title: "sentiment_analysis"
author: "GuillermoSchneider"
date: "2024-03-08"
output: html_document
---

# **PROJECT 3: Guillermo Schneider, Richie Rivera, Lucas Weyrich, Jonathan Cruz**

### Summary:
Search through reddit comments
Search for comments that include Skills
see what positive or negative words are around in those comments
average sentiment score for each Skill
sentiment analysis over time



```{r}
#install.packages("tidytext")
#install.packages("textdata")
#install.packages("tidyverse")
#install.packages("wordcloud")
#install.packages("datawizard")
#install.packages("ggrepel")
library(tidytext)
library(textdata)
library(tidyverse)
library(wordcloud)
library(caret)
library(datawizard)
library(ggrepel)
```

## https://www.tidytextmining.com/sentiment

### GRABBING SENTIMENT LABELED DICTIONARIES

**AFINN from Finn Årup Nielsen**
```{r}
afinn <- get_sentiments("afinn")
```

**bing from Bing Liu and collaborators**
```{r}
bing <- get_sentiments("bing")
```

**nrc from Saif Mohammad and Peter Turney**
```{r}
nrc <- get_sentiments("nrc")
```

```{r}
afinn_nrc_sentiments <- afinn %>% 
  inner_join(nrc) 
```
  
  
### SCRAPING THANKS TO LUCAS

**sample of 8000 posts from lucas**
```{r}
test_scrape <- read.csv("https://raw.githubusercontent.com/GuillermoCharlesSchneider/DATA-607/main/Project-3/test_scrape.csv")
```

**full 125k posts from lucas**
```{r}
full_scrape <- read.csv("https://raw.githubusercontent.com/riverar9/cuny-msds-project-3/main/part_2/reddit%20scrape.csv")
```


## UPDATED SKILLS

**Skills provided by jon:**
```{r}
Skills <- read.csv("https://raw.githubusercontent.com/GuillermoCharlesSchneider/DATA-607/main/Project-3/skills.csv")
```

**separate skills into single words, while still keeping the general skill bucket**
```{r}
Skills$word <- tolower(Skills$Skills)

Skills_single_word <- Skills %>%
  unnest_tokens(word, word)

Skills_single_word <- Skills_single_word[-c(4,9,10,11,20,21,22,23,25,28,31,40,41,42,43,46,48,50,55,57,62,65,67,71,72,75,80,83,84,92,99,136,140,141,146,147,148,150,151,152,153,154), ]
row.names(Skills_single_word) <- 1:nrow(Skills_single_word)

```

**TWO WORD SKILLS MERGED INTO ONE and trimmed (ex:data science -> datascience), multiple words per bucket. this is a stupid method, but i was too tired to figure out a new function, and i needed to look through them all anyway to see which needed to be combined and which didnt:**
```{r}
for(x in c(1,5,10,13,21,24,23,26,29,35,37,39,42,46,48,50,56,60,59,64,63,66,73,72,75,77,80,79,82,84,86,91,93,98,97,102,101,100,106,108,110)){
  Skills_single_word$word[x] <- paste(Skills_single_word$word[x],Skills_single_word$word[x+1],sep = "")
}

Skills_single_word <- Skills_single_word[-c(2,6,11,14,17,18,22,25,24,27,30,36,38,40,43,47,49,51,57,61,60,65,64,67,74,73,76,78,81,80,83,85,87,90,92,94,99,98,103,102,101,107,109,111), ]
row.names(Skills_single_word) <- 1:nrow(Skills_single_word)


```

```{r}
write.csv(Skills_single_word, "Updated_Skills.csv", row.names=FALSE)
```

## MERGED 2 WORD SKILLS (ex: data science -> datascience) IN SCRAPED REDDIT COMMENTS

### **TEST SCRAPE 8k**
```{r}
test_scrape$comment <- tolower(test_scrape$comment)
```

**test 8k data, once again im sure we could write a function, but ive already commited to this stupid copy paste, maybe one of you can make a:  gsub inputs(skills...), desired outputs (skills merged...)**
```{r}
test_scrape$comment <- gsub("data science", "datascience,",test_scrape$comment)
test_scrape$comment <- gsub("data analysis", "dataanalysis,",test_scrape$comment)
test_scrape$comment <- gsub("cloud databases", "clouddatabases",test_scrape$comment)
test_scrape$comment <- gsub("machine learning", "machinelearning",test_scrape$comment)
test_scrape$comment <- gsub("apache spark", "apachespark",test_scrape$comment)
test_scrape$comment <- gsub("pivot table", "pivottable",test_scrape$comment)
test_scrape$comment <- gsub("case studies", "casestudies",test_scrape$comment)
test_scrape$comment <- gsub("convolutional neuralnet works", "convolutionalneuralnetworks",test_scrape$comment)
test_scrape$comment <- gsub("data ethics", "dataethics",test_scrape$comment)
test_scrape$comment <- gsub("data collection", "datacollection,",test_scrape$comment)
test_scrape$comment <- gsub("data exploration", "dataexploration,",test_scrape$comment)
test_scrape$comment <- gsub("artificial intelligence", "artificialintelligence,",test_scrape$comment)
test_scrape$comment <- gsub("machine learning", "machinelearning,",test_scrape$comment)

#ive started to regret it about here
test_scrape$comment <- gsub("ask questions", "askquestions,",test_scrape$comment)
test_scrape$comment <- gsub("data driven", "datadriven",test_scrape$comment)
test_scrape$comment <- gsub("big data", "bigdata",test_scrape$comment)
test_scrape$comment <- gsub("descriptive statistics", "descriptivestatistics",test_scrape$comment)
test_scrape$comment <- gsub("recurrent neural network", "recurrentneuralnetwork",test_scrape$comment)
test_scrape$comment <- gsub("deep neural networks", "deepneuralnetworks",test_scrape$comment)
test_scrape$comment <- gsub("hyper parameter tuning", "hyperparametertuning",test_scrape$comment)
test_scrape$comment <- gsub("exploratory data analysis", "exploratorydataanalysis",test_scrape$comment)
test_scrape$comment <- gsub("neural network architecture", "neuralnetworkarchitecture",test_scrape$comment)
test_scrape$comment <- gsub("regression analysis", "regressionanalysis",test_scrape$comment)
test_scrape$comment <- gsub("data aggregation", "dataaggregation",test_scrape$comment)
test_scrape$comment <- gsub("deep learning", "deeplearning",test_scrape$comment)
test_scrape$comment <- gsub("data cleansing", "datacleansing",test_scrape$comment)
test_scrape$comment <- gsub("statistical hypothesis testing", "statisticalhypothesistesting",test_scrape$comment)
test_scrape$comment <- gsub("relational database management systems", "relationaldatabasemanagementsystems",test_scrape$comment)
test_scrape$comment <- gsub("information technology", "informationtechnology",test_scrape$comment)
test_scrape$comment <- gsub("data architecture", "dataarchitecture",test_scrape$comment)
test_scrape$comment <- gsub("process data", "processdata",test_scrape$comment)


```

**separate 8000 comments into single words**
```{r}
tidy_test_scrape <- test_scrape %>%
  unnest_tokens(word, comment)
```

**TEST_SCRAPE: filter to just comments containing skills**
```{r}
TEST <- tidy_test_scrape %>%
  inner_join(Skills_single_word) 

comment_ids <- distinct(TEST, X, Skills)

TEST2 <- filter(tidy_test_scrape, tidy_test_scrape$X %in% comment_ids$X)


TEST2 <- TEST2 %>%
  left_join(afinn) 

TEST2 <- TEST2 %>%
  left_join(bing) 

TEST2 <- TEST2 %>%
  left_join(Skills_single_word)

#MEAN excluding all non sentiment words. sum of sentiment values /  number of only sentiment words
TEST3 <- TEST2 %>%
  group_by(X) %>%
  summarize(sentiment_score = mean(value,na.rm=T))

#setting each word without a sentiment, to a 0 sentiment value
TEST2$value[is.na(TEST2$value)] <- 0 
 
#MEAN of sentiments / total words (including nonsentiments) in comment 
TEST4 <- TEST2 %>%
  group_by(X) %>%
  summarize(sentiment_score = mean(value))

TEST5 <- TEST2 %>%
  group_by(X) %>%
  summarize(sentiment_score = sum(value))
  
```





```{r}
write.csv(tidy_test_scrape, "tidy_test_scrape_merged.csv", row.names=FALSE)
```

### **FULL SCRAPE**

**full_scrape TO LOWER CASE**
```{r}
full_scrape$comment <- tolower(full_scrape$comment)
```

**CLEANING TWO WORDS TO ONE. once again no function... zzz**
```{r}
full_scrape$comment <- gsub("data science", "datascience",full_scrape$comment)
full_scrape$comment <- gsub("data analysis", "dataanalysis",full_scrape$comment)
full_scrape$comment <- gsub("cloud databases", "clouddatabases",full_scrape$comment)
full_scrape$comment <- gsub("machine learning", "machinelearning",full_scrape$comment)
full_scrape$comment <- gsub("apache spark", "apachespark",full_scrape$comment)
full_scrape$comment <- gsub("pivot table", "pivottable",full_scrape$comment)
full_scrape$comment <- gsub("case studies", "casestudies",full_scrape$comment)
full_scrape$comment <- gsub("convolutional neuralnet works", "convolutionalneuralnetworks",full_scrape$comment)
full_scrape$comment <- gsub("data ethics", "dataethics",full_scrape$comment)
full_scrape$comment <- gsub("data collection", "datacollection",full_scrape$comment)
full_scrape$comment <- gsub("data exploration", "dataexploration",full_scrape$comment)
full_scrape$comment <- gsub("artificial intelligence", "artificialintelligence",full_scrape$comment)
full_scrape$comment <- gsub("machine learning", "machinelearning",full_scrape$comment)

#ive started to regret it about here
full_scrape$comment <- gsub("ask questions", "askquestions",full_scrape$comment)
full_scrape$comment <- gsub("data driven", "datadriven",full_scrape$comment)
full_scrape$comment <- gsub("big data", "bigdata",full_scrape$comment)
full_scrape$comment <- gsub("descriptive statistics", "descriptivestatistics",full_scrape$comment)
full_scrape$comment <- gsub("recurrent neural network", "recurrentneuralnetwork",full_scrape$comment)
full_scrape$comment <- gsub("deep neural networks", "deepneuralnetworks",full_scrape$comment)
full_scrape$comment <- gsub("hyper parameter tuning", "hyperparametertuning",full_scrape$comment)
full_scrape$comment <- gsub("exploratory data analysis", "exploratorydataanalysis",full_scrape$comment)
full_scrape$comment <- gsub("neural network architecture", "neuralnetworkarchitecture",full_scrape$comment)
full_scrape$comment <- gsub("regression analysis", "regressionanalysis",full_scrape$comment)
full_scrape$comment <- gsub("data aggregation", "dataaggregation",full_scrape$comment)
full_scrape$comment <- gsub("deep learning", "deeplearning",full_scrape$comment)
full_scrape$comment <- gsub("data cleansing", "datacleansing",full_scrape$comment)
full_scrape$comment <- gsub("statistical hypothesis testing", "statisticalhypothesistesting",full_scrape$comment)
full_scrape$comment <- gsub("relational database management systems", "relationaldatabasemanagementsystems",full_scrape$comment)
full_scrape$comment <- gsub("information technology", "informationtechnology",full_scrape$comment)
full_scrape$comment <- gsub("data architecture", "dataarchitecture",full_scrape$comment)
full_scrape$comment <- gsub("process data", "processdata",full_scrape$comment)
```

**separate 125k comments into single words**
```{r}
tidy_full_scrape <- full_scrape %>%
  unnest_tokens(word, comment)
```

**FULL SCRAPE: FIND COMMENTS CONTAINING SKILLS**
```{r, include=FALSE}
#i inner joined the skills onto the full word list, so it just kept the words that matched the skills, 
comments_containing_skills_full_scrape <- tidy_full_scrape %>%
  inner_join(Skills_single_word) 

#then grabbed the distinct comment ids
comment_ids_full <- distinct(comments_containing_skills_full_scrape, X, Skills)

#then filtered the full scrape to just include comment ids that were in that list
comments_containing_skills_full_scrape <- filter(tidy_full_scrape, tidy_full_scrape$X %in% comment_ids_full$X)

write.csv(comments_containing_skills_full_scrape , "comments_containing_skills_full_scrape .csv", row.names=FALSE)


#added afinn value
comments_containing_skills_full_scrape <- comments_containing_skills_full_scrape %>%
  left_join(afinn) %>%
  left_join(Skills_single_word)

#setting each word without a sentiment, to a 0 sentiment value
comments_containing_skills_full_scrape$value[is.na(comments_containing_skills_full_scrape$value)] <- 0 
 
#MEAN of sentiments / total words (including nonsentiments) in comment 
sentiment_mean_full_scrape <- comments_containing_skills_full_scrape %>%
  group_by(X) %>%
  summarize(sentiment_score = mean(value))

#adding skill groupings to the comments, to graph it
relevancy_vs_sentiment <- comment_ids_full %>% 
  left_join(sentiment_mean_full_scrape) %>%
  left_join(Skills)

#mean of each skill group
MEAN <- comment_ids_full %>% 
  left_join(sentiment_mean_full_scrape) %>%
  group_by(Skills) %>%
  summarize(mean_score = mean(sentiment_score))

MEAN %>%
  inner_join(Skills_single_word)

MEAN$rescaled_score <- rescale(MEAN$mean_score, to = c(-1, 1))

MEAN <- Skills %>%
  left_join(MEAN)

MEAN <- MEAN[,-3]

MEAN$rescaled_score <- rescale(MEAN$mean_score, to = c(0, 1))
MEAN$RescaledRelevancy <- rescale(MEAN$Relevancy, to = c(0, 1))


```

```{r}
#adding skill groupings to the comments, to graph it
relevancy_vs_sentiment <- comment_ids_full %>% 
  left_join(sentiment_mean_full_scrape) %>%
  left_join(Skills)

```

# **GRAPHS**
```{r}
top10skillsGraph <- relevancy_vs_sentiment %>%
  filter(Skills == c("Prepare Data for Exploration","Information Technology (IT) Architecture")) 


skill_comment_count <- comment_ids_full %>%
  group_by(Skills) %>%
 count(Skills)
  
MEAN <- MEAN %>%
  left_join(skill_comment_count)

top10MEAN <- MEAN %>%
arrange(n) %>% 
   top_n(10)

top10MEAN$Skills<- str_trim(top10MEAN$Skills) 

ggplot(top10MEAN, aes(x=rescaled_score, y=RescaledRelevancy, size = n)) +
   geom_vline(xintercept = 0.5) + geom_hline(yintercept = 0.5) +
    geom_point(alpha=0.6) +
    geom_label_repel(
    label=top10MEAN$Skills,
    size=3,
    nudge_x = 0, nudge_y = 0.01)+
    lims(x=c(0,1),y=c(0,1))+
    scale_size(range = c(1.8,6.6 ), name="Count of Comments") +
    labs(x='Comparative Relevancy', y='Comparative Sentiment', title='Relevancy vs Sentiment in Most Commented Skills') 


ggplot(relevancy_vs_sentiment, aes(reorder(factor(x=Skills),Relevancy), y=sentiment_score)) +
  geom_smooth(alpha = 1/10, method = "lm", se=TRUE, color="blue", aes(group=1)) +
  geom_boxplot(varwidth = TRUE) +
  labs(x='relevancy', y='sentiment score', title='relevancy vs. sentiment Values') +
  scale_x_discrete(label=function(x) abbreviate(x, minlength=15)) +
  theme(axis.text.x = element_text(angle = 75, hjust = 1)) 
  
  


ggplot(relevancy_vs_sentiment, aes(x=Relevancy, y=sentiment_score)) +
  geom_point() +
  geom_smooth(method = "lm")+
  labs(x='relevancy', y='sentiment score', title='relevancy vs. sentiment Values') 

```




**left join sentiments into the full scrape**
```{r}
sentiment_tidy_merged_full_scrape <- tidy_full_scrape %>%
  left_join(afinn) 

sentiment_tidy_merged_full_scrape <- sentiment_tidy_merged_full_scrape %>%
  left_join(bing) 

```
**one hot encoding is a good solution for the NRC multiple sentiments per word THANK YOU LUCAS**
```{r}
#nrc$word = as.factor(nrc$word)
#onehotnrc <- predict(dummyVars(" ~ .", data = nrc), newdata = nrc)
#onehotnrc = as.data.frame(onehotnrc)


#group by sentiment
#lucas will use for nrc analysis if needed

#library(caret)
#one_hot_encoded <- dummyVars("~.", data = data)
#encoded_data <- data.frame(predict(one_hot_encoded, newdata = data))
```








**CLEANED TIDIED DATASET WITH MERGED WORDS**
```{r}
write.csv(sentiment_tidy_merged_full_scrape, "tidy_full_scrape_merged_sentiments.csv", row.names=FALSE)
```


**count of single word Skills words in the tidied scape:**
```{r}
#8000 comments
tidy_test_scrape %>%
  inner_join(Skills_single_word) %>%
  count(word, sort = TRUE) %>%
  head(10)

#125k comments
tidy_full_scrape %>%
  inner_join(Skills_single_word) %>%
  count(word, sort = TRUE) %>%
  head(10)
```


**joyful words from NRC:**
```{r}
nrc_joy <- get_sentiments("nrc") %>% 
  filter(sentiment == "joy")
```

**count of joyful words in the tidied single word scrape, matching 1 to 1 words w inner join on "word" column:**
```{r}
tidy_test_scrape %>%
  inner_join(nrc_joy) %>%
  count(word, sort = TRUE) %>%
  head(10)
```



**count of all single words**
```{r}
t <- tidy_full_scrape %>%
  count(word, sort = TRUE)
```


## **Time Series graphs (thanks LUCAS)**
```{r}

library(ggplot2)
library(zoo)

sentiment_comments_containing_skills_full_scrape <- comments_containing_skills_full_scrape %>%
  left_join(afinn) 

sentiment_comments_containing_skills_full_scrape <- sentiment_comments_containing_skills_full_scrape %>%
  left_join(bing) 

time_series_full_scrape = sentiment_tidy_merged_full_scrape %>%
  group_by(date) %>%
  summarize(positive = sum(sentiment == "positive", na.rm = TRUE), 
            negative = sum(sentiment == "negative", na.rm = TRUE)) %>%
  mutate(sentiment_value = positive - negative) %>%
  mutate(roll_avg_7 = rollmean(sentiment_value, k = 7, fill = NA)) %>%
  mutate(roll_avg_30 = rollmean(sentiment_value, k = 30, fill = NA)) %>%
  mutate(roll_avg_30_pos = rollmean(positive, k = 30, fill = NA)) %>%
  mutate(roll_avg_30_neg = rollmean(negative, k = 30, fill = NA))

time_series_skills_scrape = sentiment_comments_containing_skills_full_scrape %>%
    group_by(date) %>%
  summarize(positive = sum(sentiment == "positive", na.rm = TRUE), 
            negative = sum(sentiment == "negative", na.rm = TRUE)) %>%
  mutate(sentiment_value = positive - negative) %>%
  mutate(roll_avg_7 = rollmean(sentiment_value, k = 7, fill = NA)) %>%
  mutate(roll_avg_30 = rollmean(sentiment_value, k = 30, fill = NA)) %>%
  mutate(roll_avg_30_pos = rollmean(positive, k = 30, fill = NA)) %>%
  mutate(roll_avg_30_neg = rollmean(negative, k = 30, fill = NA))

time_series_full_scrape$date = as.Date(time_series_full_scrape$date)
time_series_skills_scrape$date = as.Date(time_series_skills_scrape$date)

ggplot(aes(x = date, y = sentiment_value), data = time_series_full_scrape) +
  geom_line() +
  theme_minimal() +
  labs(x = 'Date', y = 'Sentiment Count (Positive - Negative)', title = 'Sentiment Counts for r/DataScience and r/DataEngineer')

ggplot(aes(x = date, y = roll_avg_30), data = time_series_full_scrape) +
  geom_line() +
  theme_minimal() +
  labs(x = 'Date', y = 'Sentiment Count (Positive - Negative)', title = '30-day Rolling Mean of Sentiment for r/DataScience and r/DataEngineer')

ggplot(time_series_full_scrape, aes(x = date)) +
  geom_line(aes(y = roll_avg_30_pos, color = "Positive")) +
  geom_line(aes(y = roll_avg_30_neg, color = "Negative")) +
  labs(x = "Date", y = " Sentiment Count", title = "30-day Rolling Mean of Sentiment for r/DataScience and r/DataEngineer", color = "Sentiment") +
  scale_color_manual(values = c("Positive" = "#4CCD99", "Negative" = "#EE4266")) +
  theme_minimal()

ggplot(aes(x = date, y = sentiment_value), data = time_series_skills_scrape) +
  geom_line() +
  theme_minimal() +
  labs(x = 'Date', y = 'Sentiment Count (Positive - Negative)', title = 'Sentiment Counts for Skills in r/DataScience and r/DataEngineer')

ggplot(aes(x = date, y = roll_avg_30), data = time_series_skills_scrape) +
  geom_line() +
  theme_minimal() +
  labs(x = 'Date', y = 'Sentiment Count (Positive - Negative)', title = '30-day Rolling Mean of Sentiment for Skills in r/DataScience and r/DataEngineer')

ggplot(time_series_skills_scrape, aes(x = date)) +
  geom_line(aes(y = roll_avg_30_pos, color = "Positive")) +
  geom_line(aes(y = roll_avg_30_neg, color = "Negative")) +
  labs(x = "Date", y = " Sentiment Count", title = "30-day Rolling Mean of Sentiment for Skills in r/DataScience and r/DataEngineer", color = "Sentiment") +
  scale_color_manual(values = c("Positive" = "#4CCD99", "Negative" = "#EE4266")) +
  theme_minimal()
```



**potential word cloud code?**

library(wordcloud)
w <- sort(rowSums(t), decreasing = TRUE)
set.seed(222)
wordcloud(word = word(w),
          freq = w,
          max.words = 150,
          random.order = F,
          min.freq = 5,
          colors = brewer.pal(8, 'Dark2'),
          scale = c(5, 0.3),
          rot.per = 0.7)


