---
title: "HW3"
output: html_document
date: "2024-02-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. 
**load majors data, and install tidyverse:**
```{r}
majors <- read.csv("majors-list.csv", header=TRUE, stringsAsFactors=FALSE)
install.packages("tidyverse", repos = "http://cran.us.r-project.org")
library(tidyverse)
```

**majors that contain either "DATA" or "STATISTICS":**
```{r}
str_view(majors$Major, "DATA|STATISTICS")
```

## 2.
**START:**
```{r}
x <-
'[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"'
```

**transformations:**
```{r}
test <- str_remove_all(x, '\\d')
test <- str_remove_all(test, '\\[')
test <- str_remove_all(test, '\\]')
test <- str_remove_all(test, '\\\\')
test <- str_replace_all(test, '\\s+', "\\, ")
test <- str_replace(test, '\\, ','c(')
test <- str_c(test,')')
test
```
**GOAL:**
```{r}
desiredOutput = 'c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")'
desiredOutput
```


## 3. 

    a. (.)\1\1 --  the same three characters like AAA
    b. "(.)(.)\\2\\1" --  two characters and then reversed, like ABBA
    c. (..)\1 -- group of two characters repeated, like ABAB
    d. "(.).\\1.\\1" -- two characters, and then a third with the first on each side like "ABACA
    e. "(.)(.)(.).*\\3\\2\\1" -- atleast three chars and ending reversed like "ABCXXXXXXCBA"
    
    
## 4.

**Start and end with the same character:**

####    ^(.).*\1$


**Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)**

#### ([a-zA-Z][a-zA-Z]).*\1

**Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)**

#### ([a-zA-Z]).*\1.*\1
  
  
  
  
  