---
title: "HW5"
author: "GuillermoSchneider"
date: "2024-02-23"
output: html_document
---

# *Assignment – Tidying and Transforming Data*


```{r}
library(tidyr)
library(dplyr)
```

**read in csv:**
```{r}
airlines <- read.csv("https://raw.githubusercontent.com/GuillermoCharlesSchneider/DATA-607/main/HW5/airlines.csv")
airlines <- data.frame(airlines[-3, ])
colnames(airlines)[1:2] <- c('airline','status')
airlines[2,1] <- 'ALASKA'
airlines[4,1] <- 'AM WEST'
```


**tidy and make it long rather than wide:**
```{r}
airlines2 <- airlines %>%
  pivot_longer(
    3:7,
    names_to = "destinations", 
    values_to = "occurances"
  )


#compare within destinations
airlines2 %>% filter(status == "delayed")%>% arrange(destinations, desc(occurances))

# most delayed
airlines2 %>% filter(status == "delayed")%>% arrange(desc(occurances))

```

## **Recommend flying AM WEST.** 
**AM WEST (10.89%) has an overall slightly lower average percentage of delayed flights than ALASKA (13.27%) **
```{r}
#group  by airlines, then delay status
airlines3 <- airlines2 |> 
  group_by(airline,status) |> 
  summarize(flights = sum(occurances), .groups = 'drop') 

#add an additional column of delayed status number / total airlines flights
airlines3 <-
airlines3 |>  
group_by(airline) %>% 
mutate(percent = flights / sum(flights) * 100)

print(airlines3)
```

## **airline recommendation by destination:**
   **Los.Angeles -> AM WEST.** pretty similar delay rates, doesnt seem to matter much \
   **Phoenix -> ALASKA.** huge advantage to ALASKA, but also a tiny sample size of 12 flights \
   **San.Diego -> ALASKA.** blessed destination, least delays for either airline of all the destinations\
   **San.Francisco -> AM WEST.** sightly better chance of no delays w/ AM WEST\
   **Seattle -> AM WEST.** just asking for trouble if you fly ALASKA w/ 10x more delays\
    
```{r}
#group  by airlines, then delay status
airlines4 <- airlines2 

#add an additional column of delayed status number / total airlines flights
airlines4 <-
airlines4 |>  
  group_by(airline) %>% 
  mutate(percent = occurances / sum(occurances) * 100)

print(airlines4 %>% filter(status == "delayed") %>% arrange(destinations))


```



